Aircraft Wildlife Collisions

### 2021-07-20 draft_final.Rmd
Final draft PDF

set.seed(43)
top50 <- machines[order(-machines$n)[1:50],] %>% 
  mutate(angle = 30 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1)))
top50_aircrafts_wordcloud <- ggplot(top50) +
  aes(label = atype, size=n, color=ac_mass)+#, angle=angle) +
  geom_text_wordcloud_area(
    mask = png::readPNG(source="flugzeug6-3.png"),
    #mask = png::readPNG(source="/Users/Vy/Documents/R_Projects/Data_Visualization/flugzeug6-3.png"),
    rm_outside = TRUE) +
  scale_size_area(max_size = 3) +
  scale_color_brewer(palette="BuPu") +
  #ggtitle("top 50 aircraft models causing strikes")
  #theme(plot.title = element_text(vjust=-20)) +
  theme.title+
  labs(
    title="Top 50 aircrafts involved in collisions",
    subtitle = "Model types by number of collisions"
       )

>>>>

set.seed(43)
top50 <- machines[order(-machines$n)[1:50],] %>% 
  mutate(angle = 30 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1)))
top50_aircrafts_wordcloud <- ggplot(top50) +
  aes(label = atype, size=n, color=ac_mass)+#, angle=angle) +
  geom_text_wordcloud_area(
    #mask = png::readPNG(source="flugzeug6-3.png"),
    #mask = png::readPNG(source="/Users/Vy/Documents/R_Projects/Data_Visualization/flugzeug6-3.png"),
    rm_outside = TRUE) +
  scale_size_area(max_size = 3) +
  scale_color_brewer(palette="BuPu") +
  #ggtitle("top 50 aircraft models causing strikes")
  #theme(plot.title = element_text(vjust=-20)) +
  theme.title+
  labs(
    title="Top 50 aircrafts involved in collisions",
    subtitle = "Model types by number of collisions"
       )
